\thetitle

### 2023-06-05 introduction.tex
Fix Typo.

\item We contribute a prototypical implementation of our language
mechanism as a Coq plugin (\cref{sec:coqimpl}),
available at \url{https://anonymized-link-to-code}.
The plugin works by
compiling surface-language definitions into Coq modules parameterized by
explicit extensibility hooks.

>>>>

\item We contribute a prototypical implementation of our language
mechanism as a Coq plugin (\cref{sec:coqimpl}),
available at \url{https://github.com/DKXXXL/FPOP}.\YZ{TODO}
The plugin works by
compiling surface-language definitions into Coq modules parameterized by
explicit extensibility hooks.

### 2023-06-05 lang-design.tex
Fix Typo.

\ref{prop:detectable-partiality} is derivable for all the finitary branching inductive type\footnote{By simply enumerating through the finite domain "Bᵢ a"}---that includes all of the examples shown in this paper.

>>>>

\ref{prop:detectable-partiality} is derivable for all the finitary branching inductive type\footnote{By simply enumerating through the finite domain "Bᵢ a".}---that includes all of the examples shown in this paper.

### 2023-06-05 metatheory2.tex
Fix Typo.

We review the base MLTT fragment of \TT first.
\input{all-mltt-typing}

@@

\TT extends the MLTT in \cref{sec:mltt-full} with W-type signatures and W-types,
linkage signatures and linkages, and linkage transformers.

>>>>

We review the base MLTT fragment of \TT first. The following rules are the fully expanded version of \cref{fig:mltt-selected}, where each type (except universes) has four kinds of rules: introduction, elimination, computation and uniqueness rules. Computation rules indicate the judgemental equality when elimination rules apply to the introduction form. Uniqueness rules indicate how some terms are possibly uniquely constructed by introduction rules. The substitution rule is in the form of de Bruijn indices.

The first four rules are following the style of \citet{program2013homotopy, pfenning2009lecture}, while the substitution rules are naturally required for any language with first-class functions.
\input{all-mltt-typing}

@@

\TT extends the MLTT in \cref{sec:mltt-full} with W-type signatures and W-types,
linkage signatures and linkages, and linkage transformers. The following rules are the fully expanded version of \cref{fig:fmltt-selected}, where each type has five kinds of rules: introduction, elimination, computation, uniqueness rules and substitution lemma. 
Computation rules indicate the judgemental equality when elimination rules apply to the introduction form. Uniqueness rules indicates how some terms are possibly uniquely constructed by introduction rules. The substitution rule is in the form of de Bruijn indices.

The first four rules are following the style of \citet{program2013homotopy, pfenning2009lecture}, while the substitution rules are naturally required for any language with first-class functions.

Apart from types, we also lay out the complete version of judgements for signatures and linkage transformers. The signature judgements are also following these four parts---introduction, elimination, computation and uniqueness.
